---
title: "GSS Poster Presentation"
author: "Kathleen E. Wendt, Siqi Zhang, & Mallory J. Feldman"
date: "10/23/2019"
output: pdf_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
```

# Introduction

## Interest and need

- Brief literature review - meta-analysis, systematic review, etc.
- Need in field. See rplos folder for text query. Can `source()` script to bring in rplos info.
- Larger issue of the social science "replicability crisis."

## Logistical and methodological issues

- Possible errors and problems at every stage
- Image of data science pipeline/research workflow
- Inefficiency and disorganization (e.g., file structure; Excel)
- Misinterpretation of error-ridden psychophysiological measures

## Computational reproducibility

- R ecosystem
- Rise of data science, open science, and open source software development (e.g., Unconferences)
- Tidyverse principles
- Our answer: `psyphr` - R package suite

# Load Packages

```{r packages}
# devtools::install_github("psyphr-dev/psyphr.read")
library(psyphr.read)
library(tidyverse)
```

# Dummy Data

## Read 

```{r}
psyphr.read::MW("../data/Pilot1/Pilot_Sub1_BP_Baseline.xlsx")
```

## Transform



