---
title: "GSS Poster Presentation"
author: "Kathleen E. Wendt, Siqi Zhang, & Mallory J. Feldman"
date: "Draft by 11/04/2019"
output: pdf_document
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='figs/',
                      warning=FALSE, message=FALSE)
```

# Introduction

@iqis - can condense introductory sections into poster space by taking key concepts, words, references (can number refs like medical journals instead of APA formatting)

## A Burgeoning Field 

- There is a growing interest in including physiological measurements (i.e., psychophysiology, or study of mind and body) in social and behavioral sciences.

## Conventional Workflow 

- Most researchers do not have access to (free, open source) tools for efficient and effective psychophysiological data management.
- Current workflow: (1) process data manually in proprietary application, (2) copy-paste individual values from Excel workbook (x1000) into SPSS, (3) and hope all is well.
- **Error-ridden data produces error-driven inferences.**
- **Unstandardized formatting obstructs shareability and reproducibility.**

## The Problem

- Contemporary perspectives on the embodied mind have increased interest in psychophysiological processes and their measurement (CITE).
- Despite significant innovation (e.g., Bizzego et al 2019), this burgeoning field lacks sophisticated tools for managing the quantity and quality of psychophysiological data (e.g., Baldwin, 2017).
- Currently, most data cleaning and preprocessing requires proprietary software
These software produce several output files per-subject. These files often vary in their formatting and require extensive data wrangling.
- When conducted by hand, wrangling introduces opportunities for bias and error (CITE).
- **Error-ridden data produces error-driven inferences.**
- **Unstandardized formatting obstructs shareability and reproducibility.**

## The Solution

- R provides an existing infrastructure for open-source software development.
- We introduce a new R package suite called `psyphr`, capitalizing on larger discourses re: open science (e.g., Prlic & Proctor, 2012) and computational reproducibility (e.g., Kreibig 2017; Ince et al 2012; Piccolo et al 2016; Stodden & Miguez 2014) _pick best refs_
- This poster illustrates the purpose and functionality of our first R package within the `psyphr` suite.
- `psyphr.read` is designed to help researchers wrangle and tidy psychophysiological data from proprietary data collection systems. Currently supports output from [MindWare Technologies](https://www.mindwaretech.com/) software applications.

# Load Packages

```{r packages}
# devtools::install_github("psyphr-dev/psyphr.read")
library(psyphr.read)
library(tidyverse)
library(tibble)
library(readxl)
library(ggplot2)
```

# Example data

Would it be better to take snapshots of the file directory structure and even the Excel workbook? I am trying to think about the best way to show that these data are disorganized, messy, and in need of `psyphr` tools. I don't think it would be particularly useful to include all the code required to "wrangle" one Excel workbook.


```{r xlsx_preview}
list.files("gss_poster/data")
readxl::read_xlsx("../data/Pilot1/Pilot_Sub1_ECG_Baseline.xlsx", sheet = 1) %>%
  glimpse()
```

## Create lists of file names - @iqis, what do you think is the best way to manage the multiple person/task/stream problem? I don't think `psyphr.read::MW()` is best used on a folder split by person and task. It would be best for the user to be able to map all of the files in a study at once and have internal labels for person, task, and data stream type that can be filtered.

@wendtke This problem should be covered. If the user needs to read a bunch of files in different folders, he is encouraged to structure them as flat, with `psyphr.read::flatten_study_dir()`, then and `psyphr.read::MW_study()` can work.

```{r file_list1}
pilot1_path <- "../data/Pilot1"
list.files(pilot1_path, ".xlsx")
```

```{r file_list2}
pilot2_path <- "../data/Pilot2"
list.files(pilot2_path, ".xlsx")
```

## Use `psyphr.read::MW_study()` to read data 

```{r read_study1}
pilot1 <- psyphr.read::MW_study(pilot1_path)
```

```{r read_study2}
pilot2 <- psyphr.read::MW_study(pilot2_path)
```

## Use `psyphr.read::unnest_data()` to unnest study 

```{r unnest_study1}
pilot1_unnested <- pilot1 %>% psyphr.read::unnest_data()
```

```{r unnest_study2}
pilot2_unnested <- pilot2 %>% psyphr.read::unnest_data()
```

## HRV: Respiratory sinus arrhythmia

### Pilot 1 data preparation

```{r hrv_rsa1}
hrv1_baseline <- pilot1_unnested %>% 
  filter(format == "HRV") %>% 
  select(id_1:id_4, `HRV Stats`) %>% 
  filter(id_4 == "Baseline") %>% 
  unnest() %>% 
  filter(`Segment Duration` == "30") %>% 
  select(id_1:id_4, `Segment Number`, RSA) %>% 
  mutate(rsa_base = mean(RSA)) # calculate average baseline RSA

hrv1_rls <- pilot1_unnested %>% 
  filter(format == "HRV") %>% 
  select(id_1:id_4, `HRV Stats`) %>% 
  filter(id_4 == "RLS") %>% 
  unnest() %>% 
  filter(`Segment Duration` == "30") %>% 
  select(id_1:id_4, `Segment Number`, RSA) %>% 
  mutate(rsa_react_rls = hrv1_rls$RSA - hrv1_baseline$rsa_base) # calculate reactivity
```

## Pilot 2 data preparation

```{r hrv_rsa2}
hrv2_baseline <- pilot2_unnested %>% 
  filter(format == "HRV") %>% 
  select(id_1:id_4, `HRV Stats`) %>% 
  filter(id_4 == "Baseline") %>% 
  unnest() %>% 
  filter(`Segment Duration` == "30") %>% 
  select(id_1:id_4, `Segment Number`, RSA) %>% 
  mutate(rsa_base = mean(RSA)) # calculate average baseline RSA

hrv2_rls <- pilot2_unnested %>% 
  filter(format == "HRV") %>% 
  select(id_1:id_4, `HRV Stats`) %>% 
  filter(id_4 == "RLS") %>% 
  unnest() %>% 
  filter(`Segment Duration` == "30") %>% 
  select(id_1:id_4, `Segment Number`, RSA) %>% 
  mutate(rsa_react_rls = hrv2_rls$RSA - hrv2_baseline$rsa_base) # calculate reactivity

hrv_rls_data <- full_join(hrv1_rls, hrv2_rls)
```

## Plot RSA reactivity scores across cognitive performance task

```{r rsa_plot}
hrv_rls_data %>% 
  rename("study" = id_1,
         "subject" = id_2,
         "stream" = id_3,
         "task" = id_4) %>% 
  group_by(subject) %>% 
  ggplot(aes(x = `Segment Number`, y = rsa_react_rls, color = subject)) + 
  geom_line() +
  ylab("Respiratory sinus arrhythmia reactivity score") +
  xlab("Segment Number (30 sec)") + 
  ggtitle("Respiratory sinus arrhythmia reactivity scores across cognitive performance task by subject")
```

## IMP: Pre-ejection period 

### Pilot 1 data preparation

```{r imp_pep1}
imp1_baseline <- pilot1_unnested %>% 
  filter(format == "IMP") %>% 
  select(id_1:id_4, `Impedance Stats`) %>% 
  filter(id_4 == "Baseline") %>% 
  unnest() %>% 
  filter(`Segment Duration` == "30") %>% 
  select(id_1:id_4, `Segment Number`, PEP) %>% 
  mutate(pep_base = mean(PEP)) # calculate average baseline PEP

imp1_rls <- pilot1_unnested %>% 
  filter(format == "IMP") %>% 
  select(id_1:id_4, `Impedance Stats`) %>% 
  filter(id_4 == "RLS") %>% 
  unnest() %>% 
  filter(`Segment Duration` == "30") %>% 
  select(id_1:id_4, `Segment Number`, PEP) %>% 
  mutate(pep_react_rls = PEP - imp1_baseline$pep_base) # calculate reactivity
```

## Pilot 2 data preparation

```{r imp_pep2}
imp2_baseline <- pilot2_unnested %>% 
  filter(format == "IMP") %>% 
  select(id_1:id_4, `Impedance Stats`) %>% 
  filter(id_4 == "Baseline") %>% 
  unnest() %>% 
  filter(`Segment Duration` == "30") %>% 
  select(id_1:id_4, `Segment Number`, PEP) %>% 
  mutate(pep_base = mean(PEP)) # calculate average baseline PEP

imp2_rls <- pilot2_unnested %>% 
  filter(format == "IMP") %>% 
  select(id_1:id_4, `Impedance Stats`) %>% 
  filter(id_4 == "RLS") %>% 
  unnest() %>% 
  filter(`Segment Duration` == "30") %>% 
  select(id_1:id_4, `Segment Number`, PEP) %>% 
  mutate(pep_react_rls = PEP - imp2_baseline$pep_base) # calculate reactivity
```

```{r full_imp}
imp_rls_data <- full_join(imp1_rls, imp2_rls)
```

```{r pep_plot}
imp_rls_data %>% 
  rename("study" = id_1,
         "subject" = id_2,
         "stream" = id_3,
         "task" = id_4) %>% 
  group_by(subject) %>% 
  ggplot(aes(x = `Segment Number`, y = pep_react_rls, color = subject)) + 
  geom_line() +
  ylab("Pre-ejection period reactivity score") +
  xlab("Segment Number (30 sec)") + 
  ggtitle("Pre-ejection period reactivity scores across cognitive performance task by subject")
```
